---
title       : Titanic Survival Explorer
subtitle    : Course Project 
author      :  A. Ph. Clement
job         : 
framework   : io2012        # {io2012, html5slides, shower, dzslides, ...}
highlighter : highlight.js  # {highlight.js, prettify, highlight}
hitheme     : tomorrow      # 
widgets     : []            # {mathjax, quiz, bootstrap}
ext_widgets : {rCharts: [libraries/nvd3]}
mode        : selfcontained # {standalone, draft}
knit        : slidify::knit2slides
---

## Introduction

This application allows you to visualize the survival rate vs a set of biological and socio-economic categorical variables.

The dataset is from the <a href="https://www.kaggle.com/c/titanic-gettingStarted/data" target='_blank'>Titanic Kaggle competition</a>

--- .class #id 

## Categorical variables

You can select two different categorical variables among the following:

- Sex
- Passenger Class
- Age
- Number of Siblings/Spouses Aboard
- Number of Parents/Children Aboard
- Passenger Fare

--- .class #id 

## Example 1

Survival rate vs Sex and Passenger Class variables. 

```{r, echo = FALSE, message=F, results = 'asis', comment = NA, cache = F}
library(dplyr)
require(rCharts)

source('model.R')

options(RCHART_WIDTH = 600, RCHART_HEIGHT = 400)

totals <- train %>%
      group_by(Sex, Pclass) %>%
      summarise(total = sum(Survived), len = length(Survived), ratio = total / len)
    
totals <- totals[complete.cases(totals), ]    
    
n1 <- nPlot(ratio ~ Sex, group = 'Pclass', data = totals, type = 'multiBarChart')
n1$print('sample1')
```

--- .class #id 

## Example 2

Survival rate vs Sex and Passenger Fare variables. 

```{r, echo = FALSE, message=F, results = 'asis', comment = NA, cache = F}

totals <- train %>%
      group_by(Sex, FareSlice) %>%
      summarise(total = sum(Survived), len = length(Survived), ratio = total / len)
    
totals <- totals[complete.cases(totals), ]    
    
n2 <- nPlot(ratio ~ Sex, group = 'FareSlice', data = totals, type = 'multiBarChart')
n2$print('sample2')
```
